Data_Import

### 2023-04-03 Data_Import.Rmd
Creating the disorder variables.

       #Lets make some new variables 
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1-5",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "6-10",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "11-15", "16+"
                              )))))
# Disorder subtypes 
# Mood Disorders
# Anxiety Disorders
# Obsessive Compusive Disorders
# Personality Disorders
# Substance Use Disorders
# Trauma related disorders
# Psychotic Disorders
# Eating Disorders

@@

>>>>

#Lets make some new variables 
      #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1-5",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "6-10",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "11-15", "16+"
                              )))),
      #Disorder subtypes 
          # Mood Disorders
                     Mood_D = as.factor(
                      ifelse(
                        MDD_C ==1 | AnyBipolar_C == 1 | Bipolar1_C == 1 | Dysthymia_C == 1 |
                        OtherMood_C, 1, 0)),
          # Anxiety Disorders
                    Anxiety_D = as.factor(
                      ifelse(
                        GAD_C ==1 | Panic_C == 1 | PanicAgor_C == 1 | Agoraphobia_C == 1 |
                        Social_C == 1 | Specific_C == 1 | OtherAnx_C, 1, 0)),
          # Obsessive Compusive Disorders
                #OCD_C is for current OCD
          # Personality Disorders
                #BPD_C is for current BPD
          # Substance Use Disorders
                    Substance_D = as.factor(
                      ifelse(
                        Alcohol_C == 1 | Drug_C ==1, 1, 0)),
          # Trauma or stresor related disorders
                    Trauma_D = as.factor(
                      ifelse(PTSD_C == 1 | Adjustment_C ==1, 1,0)),
          # Psychotic Disorders
                    Psychotic_D = as.factor(
                      ifelse(
                        Schiz_C == 1 | Schizaff_C == 1 | AnyPsychotic_C ==1,1,0)),
            # Eating Disorders
                    Eating_D = as.factor(
                      ifelse(
                        AnyEating_C ==1 | Anorex_C == 1 | Bulim_C == 1 | Binge_C == 1, 1,0))
                    )
                    Disorder_Type = as.factor(

                    )

@@

#### Amount of disorders treated
```{r}
